Network Configuration Synthesis with Abstract Topologies

### 2016-11-13 paper/abstraction/paper.tex
separate analysis by all/some pairs. add valleyfree results

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Fault-tolerance analysis precision.}
  \label{fig:analysis-precision}
  \vspace{-1em}
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c | c | c | }
      \hline
      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
      & & Some & All & Some & All \\ 
      & & Pairs & Pairs & Pairs & Pairs \\ \hline

      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \xmark  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \xmark \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \xmark \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
      Dcell~\cite{dcell} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Fault-tolerance analysis precision for various topologies with shortest path routing.}
  \label{fig:analysis-precision}
  \vspace{-1em}
\end{figure}

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c | c | }
      \hline
      \textbf{Clos Variant} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
      & Some & All & Some & All \\ 
      & Pairs & Pairs & Pairs & Pairs \\ \hline

      Fattree & \cmark & \cmark & \cmark & \cmark  \\ \hline
      Facebook & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10 & \cmark & \cmark & \cmark & \cmark \\ \hline
      VL2 & \cmark & \cmark & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Fault-tolerance analysis precision for fat tree topologies with valley-free routing.}
  \label{fig:analysis-precision}
\end{figure}
